Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-18 paper/ms.tex
Add 40pc softening sentence

We used a mass resolution of $7.5\times10^3\,M_{\odot}$ for the baryonic
components (initial stellar disk, stellar bulge, and gas) and a mass resolution
of $3.75\times10^4\,M_{\odot}$ for the dark matter halo. This mass resolution is
closest to ``level 3'' in the AURIGA simulations \citep{2017MNRAS.467..179G}.
This corresponds to approximately $6.4\times10^6$ particles in the stellar disk,
$1.1\times10^6$ in the bulge, $1.2\times10^6$ in the gas disk, and
$25.3\times10^6$ in the dark matter halo. We used a softening length of
$20\,\textrm{pc}$ for all components. \edit1{This softening length is smaller
than used in the original GALAKOS model ($28\,\textrm{pc}$ in their model, but
$43.5\,\textrm{pc}$ when scaled to our mass resolution). Our smaller softening
length is consistent with other resolved ISM models \citep{2018MNRAS.480..800H,
2019MNRAS.489.4233M}.} Snapshots were saved at equal intervals of $0.005$ in the
time units of the simulation, $\textrm{kpc}/(\textrm{km}/\textrm{s})$.

>>>>

We used a mass resolution of $7.5\times10^3\,M_{\odot}$ for the baryonic
components (initial stellar disk, stellar bulge, and gas) and a mass resolution
of $3.75\times10^4\,M_{\odot}$ for the dark matter halo. This mass resolution is
closest to ``level 3'' in the AURIGA simulations \citep{2017MNRAS.467..179G}.
This corresponds to approximately $6.4\times10^6$ particles in the stellar disk,
$1.1\times10^6$ in the bulge, $1.2\times10^6$ in the gas disk, and
$25.3\times10^6$ in the dark matter halo. We used a softening length of
$20\,\textrm{pc}$ for all components. \edit1{This softening length is smaller
than used in the original GALAKOS model ($28\,\textrm{pc}$ in their model, but
$43.5\,\textrm{pc}$ when scaled to our mass resolution). Our smaller softening
length is consistent with other resolved ISM models \citep{2018MNRAS.480..800H,
2019MNRAS.489.4233M}. We reran our fiducial SMUGGLE run with $40\,\textrm{pc}$
softening and found no difference in the pattern speed evolution of the bar.}
Snapshots were saved at equal intervals of $0.005$ in the time units of the
simulation, $\textrm{kpc}/(\textrm{km}/\textrm{s})$.
